---
title: "Graphs"
author: "Agnieszka Kubica"
date: "`r Sys.Date()`"
output: html_document
---

# TO DO
- add outlets by matching headlin

```{r}
library(tidyverse)
```

```{r}
data <- read_csv("results.csv")
data_outlets <- read_csv("News_China_Africa.csv") |>
  select(outlet, headline)


# add outlet
data <- merge(data,data_outlets,by="headline")



head(data)
head(data_outlets)
```

# topic per country
```{r}
ggplot(data)+
  aes(x = topic_label, fill = label)+
  geom_bar()
```
- topic 5, 7 and 1 much more frequent in Ghana
- topic 8,4,9,6 more popular in Nigeria 


# Topics per outlet
```{r}
ggplot(data)+
  aes(x = topic_label, fill = outlet)+
  geom_bar()
```
- some topics more frequent than others in general as main topic
- topic five is overly represented by News Ghana
- topic eigth is overly represented by News Ghana

```{r}
ggplot(data)+
  aes(colour = topic_label, x = outlet)+
  geom_bar()
```

# Sentiments per country
```{r}
ggplot(data)+
  aes(x = label, fill = sentiment)+
  geom_bar()
```


# Sentiments per outlet
```{r}
ggplot(data)+
  aes(x = outlet, fill = sentiment)+
  geom_bar()
```
```{r}
data |>
  mutate(is_positive = ifelse(sentiment == "POSITIVE", TRUE, FALSE))|>
  group_by(outlet) |>
  summarise(ratio_sentiment = sum(is_positive)/ sum(!is_positive)) |>
  ungroup()|>
  ggplot()+
  aes(x = outlet, y  = ratio_sentiment)+
  geom_col()
```
- actually the way higher overal positive apprach to China stems from News Ghana position

# Topics and sentiments

```{r}
ggplot(data)+
  aes(x = topic_label, fill = sentiment)+
  geom_bar()+
  facet_wrap(~label)
```
```{r}
ggplot(data)+
  aes(x = topic_label, fill = sentiment)+
  geom_bar()+
  facet_wrap(~outlet)
```



